Advances in Robust Positive Invariant Set Computation

### 2015-03-03 draft.tex
Moved pictures to local directory.
Added abstract.

\documentclass[letterpaper, 10pt, conference]{ieeeconf/ieeeconf} % Change font size to 9pt

@@

\begin{abstract}

\end{abstract}

>>>>

\documentclass[letterpaper, 10pt, conference]{ieeeconf} % Change font size to 9pt

@@

\begin{abstract} 
In this paper we introduce methods of deriving and computing maximal positive robust invariant
sets for linear discrete time systems with additive uncertainty. We consider two different sets of
uncertainties, state dependent uncertainty which allows us to handle multiplicative as well as
linearised systems easily, and scaled sets of uncertainty. We provide the framework for the analytic
treatment of both and illustrate their benefits in two numerical examples.
\end{abstract}
